\documentclass{letter}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{letter}{}
    \opening{To Whom It May Concern,}

    This letter to certify that \textbf{YourName}, an undergraduate student at Southern University of Science and Technology (SUSTech), Shenzhen, China, and a member of the \textbf{XXX Team} in XXXX, has earned multiple honors in recognition of his athletic achievements.

\begin{itemize}
    \item \textbf{2024-2025 Academic Year:}
    \begin{itemize}
        \item SUSTech Outdoor Fitness Challenge: X Prize for completing a total distance of 100 km in jogging over three months, awarded by SUSTech.
        \item SUSTech 500m Rowing Ergometer Competition: X Place (X/X) in the Men's Division with a time of X min X sec, awarded by SUSTech.
        \item SUSTech Pull-Up Challenge: X Place in the Men's Division with X pull-ups, awarded by SUSTech.
    \end{itemize}
    
    \item \textbf{2023-2024 Academic Year:}
    \begin{itemize}
        \item SUSTech Spring Sports Games: X Place (X/X) in the Soft Fitness Challenge, comprising BMI, Vital Capacity, Sit-and-Reach, and Standing Long Jump assessments, awarded by SUSTech.
        \item SUSTech Pull-Up Challenge: X Place in the Men's Division with X pull-ups, awarded by SUSTech.
        \item SUSTech 500m Rowing Ergometer Competition: First Place (X/X) in the Men's Division with a time of X min X sec, awarded by SUSTech.
        \item SUSTech Swimming Competition: X Place in the Men's 50m Breaststroke with a time of X sec, awarded by SUSTech.

        \item SUSTech Swimming Competition: X Place in the Men's 50m Butterfly with a time of X sec, awarded by SUSTech.
    \end{itemize}
    
    \item \textbf{2022-2023 Academic Year:}
    \begin{itemize}
        \item SUSTech Spring Sports Games: X Place in the Men's High-Five Push-Up Challenge with X repetitions, awarded by SUSTech.
        \item SUSTech Swimming Competition: X Place in the Men's 50m Breaststroke with a time of X sec, awarded by SUSTech.
    \end{itemize}
\end{itemize}

    \vspace{1cm}
    Sincerely, \\
    \vspace{0.5cm}
    
    Center for Physical Education\\
    Southern University of Science and Technology (SUSTech) \\
    1088 Xueyuan Avenue, Nanshan District \\
    Shenzhen, Guangdong 518055, P.R. China \\
    {sports@sustech.edu.cn}
 
\end{letter}

\end{document}